Verifying Demonstrations

### 2017-09-21 SystemModel.tex
Clarifies intro to assumptions

We assume that every participant has a device similar to a smartphone.
(This means that we essentially provide a lower bound for the participation 
count, since some participants might not have any smartphone.)
It must be a portable device which can perform cryptographic operations and 
communicate with other devices during the protest, e.g.\ through an ad-hoc 
network.
I.e.\ no connection to the Internet is necessary during the protest.
During the protest these devices are computationally limited by their 
batteries.
Before and after the protest, we assume that the devices have Internet 
connections and are not computationally limited by any battery.

@@

We further assume that every participant has a digital certificate signed by 
some logically centralized certificate authority.
E.g.\ that we can use the cryptographic keys stored in the chip of the national 
identity card or passport.
We need this to prevent Sybil attacks~\cite{SybilAttack}.
\begin{frame}
\begin{remark}
  I.e.\ provided we can prevent Sybil.
\end{remark}
\end{frame}

>>>>

We assume that every participant has a device similar to a smartphone.
Throughout this text, when we refer to a participant, say Alice, we actually 
mean a principal which can perform cryptographic operations and communicate with 
other local devices on Alice's behalf.
(This means that we essentially provide a lower bound for the participation 
count, since some participants might not have such a device.)

\mode<presentation>{%
\begin{frame}
  \begin{center}
    Alice $:=$ Alice's cryptographic device
  \end{center}
\end{frame}
}

No connection to any global network the Internet is necessary during the 
protest.
During the protest these devices are computationally limited by their 
batteries.
Before and after the protest, we assume that the devices have Internet 
connections and are not computationally limited by any battery.

@@

We further assume that every participant has a digital certificate signed by 
some logically centralized certificate authority.
E.g.\ that we can use the cryptographic keys stored in the chip of the national 
identity card or passport.
We need this to prevent Sybil attacks~\cite{SybilAttack}.
